Create CHaMP map

### 2020-12-02 analysis/R_scripts/compile_wtsd_bndry.Rmd
updated R notebook for making watershed map. Changed what file types to save, deleted some obsolete versions.

# set default theme for ggplot
theme_set(theme_bw())
# setwd('analysis/R_scripts')
```

@@

```{r}
champ_wtsds = read_rds('../data/derived_data/champ_wtds.rds')
river_lines = QRFcapacity::get_flowlines(stream_order = 6,
                                         champ_wtsds %>%
                                           st_union() %>%
                                           st_make_grid(n = 1)) %>%
            filter(!grepl('^1701', reachcode),
                   !grepl('^171', reachcode))

@@

# save a couple versions
ggsave('../figures/ChampWtds.svg',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.png',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.tiff',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.jpeg',
       wtsd_map,
       dpi = 600,
       height = 6,
       width = 6)
```

>>>>

# set default theme for ggplot
theme_set(theme_bw(base_family = "Helvetica"))
# setwd('analysis/R_scripts')
```

@@

```{r}
champ_wtsds = read_rds('../data/derived_data/champ_wtds.rds')
river_lines = QRFcapacity::get_flowlines(stream_order = 6,
                                         champ_wtsds %>%
                                           st_union() %>%
                                           st_make_grid(n = 1)) %>%
            filter(!grepl('^1701', REACHCODE),
                   !grepl('^171', REACHCODE))

@@

# save a couple versions
for(file_ext in c("png", 'pdf', 'tiff')) {
  ggsave(paste0('../figures/ChampWtds.', file_ext),
       wtsd_map,
       dpi = 400,
       height = 6,
       width = 6)
}
